A Logistic Regression Approach to CoIL Challenge 2000

### 2019-11-12 final project/Manuscript.tex
Updated final project's data dictionary

>>>>

\hypertarget{data-dictionary}{%
\subsection{Data Dictionary}\label{data-dictionary}}

\begin{center}
\begin{ThreePartTable}
\begin{longtable}{ll}\noalign{\getlongtablewidth\global\LTcapwidth=\longtablewidth}
\caption{\label{tab:unnamed-chunk-3}Data Dictionary}\\
\toprule
Name & \multicolumn{1}{c}{Description}\\
\midrule
MOSTYPE & Customer Subtype\\
MAANTHUI & Number of houses\\
MGEMOMV & Avg size household\\
MGEMLEEF & Avg age\\
MOSHOOFD & Customer main type\\
MGODRK & Roman catholic\\
MGODPR & Protestant\\
MGODOV & Other religion\\
MGODGE & No religion\\
MRELGE & Married\\
MRELSA & Living together\\
MRELOV & Other relation\\
MFALLEEN & Singles\\
MFGEKIND & Household without children\\
MFWEKIND & Household with children\\
MOPLHOOG & High level education\\
MOPLMIDD & Medium level education\\
MOPLLAAG & Lower level education\\
MBERHOOG & High status\\
MBERZELF & Entrepreneur\\
MBERBOER & Farmer\\
MBERMIDD & Middle management\\
MBERARBG & Skilled labourers\\
MBERARBO & Unskilled labourers\\
MSKA & Social class A\\
MSKB1 & Social class B1\\
MSKB2 & Social class B2\\
MSKC & Social class C\\
MSKD & Social class D\\
MHHUUR & Rented house\\
MHKOOP & Home owners\\
MAUT1 & 1 car\\
MAUT2 & 2 cars\\
MAUT0 & No car\\
MZFONDS & National Health Service\\
MZPART & Private health insurance\\
MINKM30 & Income < 30.000\\
MINK3045 & Income 30-45.000\\
MINK4575 & Income 45-75.000\\
MINK7512 & Income 75-122.000\\
MINK123M & Income >123.000\\
MINKGEM & Average income\\
MKOOPKLA & Purchasing power class\\
PWAPART & Contribution private third party insurance\\
PWABEDR & Contribution third party insurance (firms)\\
PWAAND & Contribution third party insurane (agriculture)\\
PPERSAUT & Contribution car policies\\
PBESAUT & Contribution delivery van policies\\
PMOTSCO & Contribution motorcycle/scooter policies\\
PVRAAUT & Contribution lorry policies\\
PAANHANG & Contribution trailer policies\\
PTRACTOR & Contribution tractor policies\\
PWERKT & Contribution agricultural machines policies\\
PBROM & Contribution moped policies\\
PLEVEN & Contribution life insurances\\
PPERSONG & Contribution private accident insurance policies\\
PGEZONG & Contribution family accidents insurance policies\\
PWAOREG & Contribution disability insurance policies\\
PBRAND & Contribution fire policies\\
PZEILPL & Contribution surfboard policies\\
PPLEZIER & Contribution boat policies\\
PFIETS & Contribution bicycle policies\\
PINBOED & Contribution property insurance policies\\
PBYSTAND & Contribution social security insurance policies\\
AWAPART & Number of private third party insurance\\
AWABEDR & Number of third party insurance (firms)\\
AWALAND & Number of third party insurane (agriculture)\\
APERSAUT & Number of car policies\\
ABESAUT & Number of delivery van policies\\
AMOTSCO & Number of motorcycle/scooter policies\\
AVRAAUT & Number of lorry policies\\
AAANHANG & Number of trailer policies\\
ATRACTOR & Number of tractor policies\\
AWERKT & Number of agricultural machines policies\\
ABROM & Number of moped policies\\
ALEVEN & Number of life insurances\\
APERSONG & Number of private accident insurance policies\\
AGEZONG & Number of family accidents insurance policies\\
AWAOREG & Number of disability insurance policies\\
ABRAND & Number of fire policies\\
AZEILPL & Number of surfboard policies\\
APLEZIER & Number of boat policies\\
AFIETS & Number of bicycle policies\\
AINBOED & Number of property insurance policies\\
ABYSTAND & Number of social security insurance policies\\
CARAVAN & Number of mobile home policy\\
\bottomrule
\end{longtable}
\end{ThreePartTable}
\end{center}
